{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-14 thesis/intro.tex
#NewThesisStatement

\begin{center}
	% TODO: this sux, fix it
	{\em Thanks to the new algorithms, heuristics, and concurrency models I have developed,
	stateless model checking is an appropriate and accessible concurrency testing technique
	for programmers in both educational and real-world settings.}
\end{center}

>>>>

\begin{center}
	{\em Combining both theoretically-founded automatic reduction techniques
	and user-informed heuristic ones,
	stateless model checking can sufficiently mitigate exponential explosion
	to be a practical testing technique even for inexperienced users.}
\end{center}
